Collective behavior of Suspended Janus Particles via an Integral Equation Method

### 2022-05-14 doc/PRF2022/PRF_main.tex
updates

%Consider the energy profiles for two simulations where the centor of mass is on and off the origin.
%The 
%
%\begin{figure}
%  \begin{center}
%  \includegraphics[width=0.4\textwidth]{shear_energy1.jpg}
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:shear_energy1} Energy profiles tracked during the simulations using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
%\end{figure}

>>>>

Consider the energy profiles for two simulations where the centor of mass is on and off the origin.
Figure~\ref{fig:shear_energy1} shows numerical results for both energy profiles and magnitude of energy differences is significantly large when there is a large deformation, for instance, the case when a multi-lamellar structure deformed to a pancake shape.

\begin{figure}
  \begin{center}
  \includegraphics[width=0.5\textwidth]{shear_energy1.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_energy1} Energy profiles tracked during the simulations using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}
